Linear Algebra as a Unifying Theory\\of Wireless Workload Modeling

### 2008-02-07 paper.tex
Added plots!

\begin{figure*}[htb]
\subfloat[\textbf{Application:} Average End-to-End Delay]%
{\includegraphics[width=7in]{plots/Application/delay.pdf}}
\subfloat[\textbf{Application:} Average Received Throughput]%
{\includegraphics[width=7in]{plots/Application/throughput.pdf}}
\subfloat[\textbf{Application:} Total Received Data]%
{\includegraphics[width=7in]{plots/Application/total_recv_packets.pdf}}
\subfloat[\textbf{Network:} AODV Control Overhead]%
{\includegraphics[width=7in]{plots/Network/control_packets.pdf}}
\subfloat[\textbf{Link:} 802.11 Control Overhead]%
{\includegraphics[width=7in]{plots/Link/overhead.pdf}}%
\caption{Box-and-whisker plots of log-ratio error values for all metrics and traffic models. The lower axis indicates the log-ratio, while the upper axis shows raw ratio values. Each box contains the central majority of log-ratio values: the left and right bounds are at the $25^\text{th}$ and $75^\text{th}$ percentiles. The dark middle line indicates the median value, while the diamond marks the mean. The whiskers (dotted lines) extend to the furthest non-outlier values, while the points beyond that are outliers. The notch in the middle of each bar indicates a $95\%$ confidence interval for the true underlying median value; if two notches do not overlap, they are very unlikely to have the same median.}
\label{fig:box-plots}
\vspace{-1.25em}
\end{figure*}

>>>>

\begin{sidewaysfigure*}
%\begin{figure*}[htb]
\subfloat[\textbf{Application:} Average End-to-End Delay]%
{\includegraphics[width=4.6in]{plots/Application/delay.pdf}}
\subfloat[\textbf{Application:} Average Received Throughput]%
{\includegraphics[width=4.6in]{plots/Application/throughput.pdf}}
\subfloat[\textbf{Application:} Total Received Packets]%
{\includegraphics[width=4.6in]{plots/Application/total_recv_packets.pdf}}
\subfloat[\textbf{Network:} AODV Control Overhead]%
{\includegraphics[width=4.6in]{plots/Network/control_packets.pdf}}
\subfloat[\textbf{Network:} Packets Dropped in Routing Queue]%
{\includegraphics[width=4.6in]{plots/Network/dropped.pdf}}
\subfloat[\textbf{Link:} 802.11 Control Overhead]%
{\includegraphics[width=4.6in]{plots/Link/overhead.pdf}}%
\caption{Box-and-whisker plots of log-ratio error values for all metrics and traffic models. The lower axis indicates the log-ratio, while the upper axis shows raw ratio values. Each box contains the central majority of log-ratio values: the left and right bounds are at the $25^\text{th}$ and $75^\text{th}$ percentiles. The dark middle line indicates the median value, while the diamond marks the mean. The whiskers (dotted lines) extend to the furthest non-outlier values, while the points beyond that are outliers. The notch in the middle of each bar indicates a $95\%$ confidence interval for the true underlying median value; if two notches do not overlap, they are very unlikely to have the same median.}
\label{fig:box-plots}
%\vspace{-1.25em}
%\end{figure*}
\end{sidewaysfigure*}
